### 2023-08-30 appendixPN.tex
section
up

For the sake of clarity \alain{bof, une autre raison?}, we will use reset Petri nets rather than reset-VASS.

@@

We describe therein how to adjust Theorem~5.5 \alain{que dit le theorem 5.5 ?}from \cite{peterson1981petri} reducing the {\em zero-reachability} problem to {\sc $t$-liveness} in reset Petri nets. \\

>>>>

For the sake of clarity \alain{bof, une autre raison?}, we will use reset Petri nets \cite{dufourd1998reset} rather than reset-VASS.

@@

We describe therein how to adjust Theorem~5.5 \alain{que dit le theorem 5.5 ?}\mathieu{reachability se réduit à liveness pour les Petri nets}from \cite{peterson1981petri} reducing the {\em zero-reachability} problem to {\sc $t$-liveness} in reset Petri nets. \\
